---
title: "Shiny Project_DDP"
author: "HKI"
date: "December 1, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Intro

This is a presentation for the Coursera Developing Data Products 

Instructions:

1. Write a shiny application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link 
4. Share your server.R and ui.R code on github


## The application and its uage

I used the Wage data set from datasets(R) , in order to  fit linear modeal using age as predictor and
wage as outcome. A slider in the shiny app is implemented and the user is able to choose the numerical value of the predictor , ranged from 18 to 80.

The application is deployed on: https://123hki.shinyapps.io/project_ddp/
        
Shiny scripts could be found here: https://github.com/icound/DDP
        

## Summary of the data

```{r wage, echo = TRUE}
library(ISLR)
summary(Wage$age)
summary(Wage$wage)
```

## Slide with Plot

```{r pressure}
plot(Wage$age, Wage$wage, xlab = "Age", 
                     ylab = "Wage", bty = "n", pch = 16
                   )
               
                        abline(lm(wage~age, data=Wage), col = "red", lwd = 2)
               
                        legend(25, 250, "Model  Prediction", pch = 16, 
                               col = "red", bty = "n", cex = 1.2)
                
```

